---
title: "run.Rmd"
author: "BCM MSPC"
date: '`r Sys.Date()`'
output: html_document
params:
  volcanodir: none
  rankfiledir: none
  gct_path: none
  ranks_from: "volcano"  # choices are volcano and gct
  species: "Homo sapiens"
  genesets_json: >
    [
      {"category": "H", "subcategory": ""},
      {"category": "C2", "subcategory": "CP:KEGG"},
      {"category": "C2", "subcategory": "CP:REACTOME"},
      {"category": "C5", "subcategory": "GO:MF"},
      {"category": "C5", "subcategory": "GO:BP"},
      {"category": "C5", "subcategory": "GO:CC"}
      /* {"category": "C2", "subcategory": "CP:KEGG"}
      */
    ]

---

# setup

```{r setup, include=TRUE}
library(purrr) # for map()
library(magrittr)
library(ggplot2)
library(fs) # for dir_ls()
library(fgsea)
library(dplyr)
library(msigdbr)
library(stringr)
library(readr)
library(tidyr)
library(tictoc)
library(ggrepel)
#knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.path = 'bcm_gsea_figures')

library(future)
n_cores <- future::availableCores() - 1
future::plan(future::multisession, workers=min(n_cores, 8) )

source("./R/io.R")
source("./R/geneset_utils.R")
source("./R/fgsea.R")
source("./R/plot.R")
```
# explanations

```{r, label=test, eval=F, include=T}
data <- simulate_preranked_data()
geneset <- .GlobalEnv$get_collection("H", "")
geneset_list <- .GlobalEnv$genesets_df_to_list(geneset)
#named_data = list(data=data)
rankobj <- ranks_dfs_to_lists(list(data))

.res <- rankobj[[1]] %>% run_one(geneset_list)
.name <- .res[1, 'pathway'][[1]]

enplot_data <- plotEnrichmentData(geneset_list[[.name]], rankobj[[1]])

.rnkorder <- -rankobj[[1]] %>% (rank)
rankobj[[1]]['rank'] <- .rnkorder

```

## run these to examine what genesets are availabel from msigdbr


```{r, eval=F, include=T}
msigdbr::msigdbr_species()
```

```{r, eval=F, include=T}

msigdbr::msigdbr_collections()
```

# execution

## load gene sets

```{r, label='load params'}

genesets_of_interest <- jsonlite::parse_json(params$genesets_json)
species <- params$species

#SPECIES <- "Homo sapiens" # or "Mus musculus" or Saccharomyces cerevisiae, and others
# genesets_of_interest %>% purrr::map(~{print(.x$category); print(.x$subcategory)})

```


```{r, label='get genesets'}
list_of_geneset_dfs <- genesets_of_interest %>% .GlobalEnv$get_collections()
geneset_lists <- list_of_geneset_dfs %>% purrr::imap( ~.GlobalEnv$genesets_df_to_list(.x) )
```

```{r, label='convert geneset objects'}
pathways_list_of_lists <-
  list_of_geneset_dfs %>% purrr::map(.GlobalEnv$genesets_df_to_list)
```



## prepare ranks

```{r, label='load ranks'}

if ( (!file.exists(params$volcanodir)) &
    (!file.exists(params$gct_path)) &
     (!file.exists(params$rankfiledir))
){
  print("no files present")
  knitr::knit_exit()
}


```



```{r, label='prepare ranks'}

rankfiledir <- params$rankfiledir
volcanodir <- params$volcanodir
gct_path <- params$gct_path
ranks_from <- params$ranks_from
if ( length(fs::dir_ls(rankfiledir, fail=F))==0 ){
  #print('yes')
  if ( ranks_from == "volcano" ){
    rnkdfs <- .GlobalEnv$create_rnkfiles_from_volcano(volcanodir, value_col = "signedlogP")
    }
  if ( ranks_from == "gct" ){
    rnkdfs <- .GlobalEnv$create_rnkfiles_from_emat(gct_path, apply_z_score = T)
    }
  rnkdfs %>% .GlobalEnv$write_rnkfiles(dir = rankfiledir)
} #else{

# always reload rank files from new location to ensure proper format
# any format / name issues are fixed in the create_rnkfiles func
rnkfiles <- dir_ls(rankfiledir, pattern = ".rnk$", fail=F)
rnkdfs <- rnkfiles %>% .GlobalEnv$load_rnkfiles()
  #print('no')
#}
names(rnkdfs) <- names(rnkdfs) %>% fs::path_file() %>% fs::path_ext_remove()

ranks_list <- rnkdfs %>% .GlobalEnv$ranks_dfs_to_lists()
```


# run fgsea
```{r, label='run fgsea'}

results_list <- .GlobalEnv$run_all_pathways(pathways_list_of_lists, ranks_list, parallel=T) # parallel if you c

```



## explore the results

results list contains a named list of pathways

```{r}
names(results_list)
```

which contain a named list of statistics

```{r}
names(results_list[[1]])
```

```{r}
head(results_list[[1]] [[1]] )
```



## making plots


```{r}
results_list[[1]] [[1]] %>%
  arrange(pval) %>%
  head(20) %>%
  .GlobalEnv$barplot_with_numbers()
```
## plotting all barplots for each comparison within one geneset
```{r}
results_list[[1]] %>% imap(
  ~ {
    sel <- .x %>% arrange(pval) %>% head(20)
    .title <- .y %>% fs::path_file() %>% fs::path_ext_remove() #%>% gsub(pattern="_", replacement=" ", x=.)
    .GlobalEnv$barplot_with_numbers(sel, title=.title, use_custom_labeller=T)
  }
)
```

## plotting all barplots for each comparison across all genesets
```{r, fig.width=10, fig.height=8}

results_list %>% imap(
  ~{
    pathway <- .y
    list_of_comparisons <- .x
    list_of_comparisons %>% imap(
      ~ {
          dataframe <- .x
          comparison_name <- .y
          sel <- dataframe %>% arrange(pval) %>% head(20)
          .title <- comparison_name #%>% fs::path_file() %>% fs::path_ext_remove() #%>% gsub(pattern="_", replacement=" ", x=.)
          p <-.GlobalEnv$barplot_with_numbers(sel, title=.title, use_custom_labeller=T)
          return(p)
      }
    )
  }
)

```

## plot facetted barplot across genesets

prewritten function to merge gsea results across comparisons and make faceted barplot
```{r, fig.width=12, fig.height=12}


results_list %>%
  .GlobalEnv$process_results_across_rnks()


```

## heatmap of results
```{r}

all_res <- .GlobalEnv$concat_results_all_collections(results_list)

```


```{r, fig.width=10, fig.height=12}
.metadata <- gct@cdesc
all_res$H_ %>% .GlobalEnv$plot_results_one_collection(., metadata = .metadata, cut_by = 'group')
```

```{r, fig.width=10, fig.height=12}
.metadata <- gct@cdesc
all_res$`C5_GO:BP` %>% .GlobalEnv$plot_results_one_collection(., metadata = .metadata, cut_by = 'group')
```


```{r, fig.width=10, fig.height=12}
.metadata <- gct@cdesc
heatmaps <- all_res %>% .GlobalEnv$plot_results_all_collections(metadata=.metadata, cut_by='group')
```



## curve exploration


```{r, eval=F}
# Adjusting the formula with guessed parameters for a clearer sigmoid fit
# Example: a simple sigmoid with steepness and midpoint adjustments
# Ensure that you replace `.res2` and `pval` according to your actual data frame and variable names if they differ
sig_approx <- function(x) (-1 / (1 + exp(-4.1 * (x - 1.0))) + 1 )

ggplot(.res2, aes(x = abs(NES), y = pval)) +
  geom_point() +
  stat_function(fun = sig_approx,   # Adjust -0.1 (steepness) and 5 (midpoint) as needed
                color = "blue") +
  ggtitle("Fitting a Sigmoid Function")
```
```{r, eval=F}

sig_approx <- function(x) (-1 / (1 + exp(-4.1 * (x - 1.0))) + 1 )
sig_approx2 <- function(x) 1 / sig_approx
sig_approx2 <- function(x) (1 + exp(-1.1 * (x - 1.0)  ) -1 )

ggplot(.res2, aes(y = abs(NES), x = pval)) +
  geom_point() +
  stat_function(fun = sig_approx2,   # Adjust -0.1 (steepness) and 5 (midpoint) as needed
                color = "blue") +
  ggtitle("Fitting a Sigmoid Function")
```


## plot large tabular plots

this function may be moved out
```{r, fig.width=10, fig.height=12}

tic()

process_results_for_each_rank <- function(results_list, ranks_list, pathways_list) {
  # Ensure names are aligned and iterate over them
  pathway_names <- names(results_list)

  map(pathway_names, ~{
    geneset_name <- .x
    fgsea_res_list <- results_list[[geneset_name]]
    genesets <- pathways_list[[geneset_name]]

    # Now, iterate over each rank file within this pathway category
    map(names(ranks_list), function(rank_name) {
      rankobj <- ranks_list[[rank_name]]
      # Generate a unique identifier for this plot/table, e.g., combining pathway name and rank file name
      rank_name_nice <- rank_name %>% fs::path_file() %>% fs::path_ext_remove()
      plot_id <- paste(geneset_name, rank_name_nice, sep = "_")


      .fgsea_res <- fgsea_res_list[[rank_name]]
      p <- plot_table(fgsea_res = .fgsea_res,
                 ranks = rankobj,
                 pathways = genesets,
                 gsea_param=0.5,
        )

      # outpath <- file.path(ENPLOT_BASEDIR, make.names(geneset_name), make.names(rank_name_nice))
      #if (!fs::dir_exists(outpath)) fs::dir_create(outpath)

      # print(p)
      return(p)

      # c(".png", ".pdf") %>% purrr::walk(
      # ~ggsave(filename = paste0(make.names(geneset_name), "_toptable", "_gseaparam.5", .x),
      #        path = outpath,
      #        dpi = 300,
      #        width = 19,
      #        height=12,
      #        )
      # )


    })

  })
}

res <- process_results_for_each_rank(
  results_list = results_list,
  ranks_list = ranks_list,
  pathways_list = geneset_lists
)

toc()

```


```{r, fig.width=10, fig.height=12}

tic()

process_results_for_each_rank <- function(results_list, ranks_list, pathways_list) {
  # Ensure names are aligned and iterate over them
  pathway_names <- names(results_list)

  # furrr::future_map(pathway_names, ~{
  purrr::map(pathway_names, ~{
    geneset_name <- .x
    fgsea_res_list <- results_list[[geneset_name]]
    genesets <- pathways_list[[geneset_name]]

    # Now, iterate over each rank file within this pathway category
    #map(names(ranks_list), function(rank_name) {
    # furrr::future_map(names(ranks_list), function(rank_name) {
    furrr::future_imap(ranks_list, function(rankobj, rank_name) {
      # rankobj <- ranks_list[[rank_name]]
      # Generate a unique identifier for this plot/table, e.g., combining pathway name and rank file name
      rank_name_nice <- rank_name %>% fs::path_file() %>% fs::path_ext_remove()
      plot_id <- paste(geneset_name, rank_name_nice, sep = "_")


      .fgsea_res <- fgsea_res_list[[rank_name]]
      p <- plot_table(fgsea_res = .fgsea_res,
                 ranks = rankobj,
                 pathways = genesets,
                 gsea_param=0.5,
        )

      outpath <- file.path(ENPLOT_BASEDIR, make.names(geneset_name), make.names(rank_name_nice))
      if (!fs::dir_exists(outpath)) fs::dir_create(outpath)

      # print(p)
      return(p)
      # c(".png", ".pdf") %>% purrr::walk(
      # ~ggsave(filename = paste0(make.names(geneset_name), "_toptable", "_gseaparam.5", .x),
      #        path = outpath,
      #        dpi = 300,
      #        width = 19,
      #        height=12,
      #        )
      # )


    })

  })
}

res <- process_results_for_each_rank(
  results_list = results_list,
  ranks_list = ranks_list,
  pathways_list = geneset_lists
)

toc()

#76.388
```

## examine rankorder


```{r}
ranks_list %>% names
list_of_geneset_dfs %>% names

#rankorder <- .GlobalEnv$get_rankorder(ranks_list[[1]], geneset_lists[[1]][[1]]  )


rankorder <- .GlobalEnv$get_rankorder(ranks_list[[1]], geneset_lists$H_$HALLMARK_ADIPOGENESIS  ) %>% filter(!is.na(stat_tick))
rankorder %>% dim


rankorder2 <- rankorder %>%
  left_join(
    list_of_geneset_dfs$H_ %>% filter(gs_name == "HALLMARK_ADIPOGENESIS") %>% distinct(entrez_gene, .keep_all = T) %>%  mutate(entrez_gene = as.character(entrez_gene)), by = c('id' = 'entrez_gene')
)

( dim(rankorder)[1] == dim(rankorder2)[1] )

rankorder <- rankorder2


```

```{r, fig.width=10, fig.height=8}


es_min <- rankorder %>% pull(ES) %>% min(na.rm=T)
es_max <- rankorder %>% pull(ES) %>% max(na.rm=T)


make_selection <- function(x){
  .first <- which(x$ES == es_min)
  .second <- which(x$ES == es_max)
  .top <- x %>% arrange(rank) %>% head(.first)
  .bot <- x %>% arrange(rank) %>% tail(dim(x)[1] - .second)
  return(bind_rows(.top, .bot))
}
```
```{r, fig.width=10, fig.height=8}

rankorder %<>% arrange(stat_tick)
rankorder %>%
  edgeplot1() +
  geom_text_repel(data = . %>% make_selection , aes(label = gene_symbol ), max.overlaps = Inf  )
```



```{r, fig.width=12, fig.height=10}


rankorder_all <- .GlobalEnv$get_rankorder(ranks_list[[1]], geneset_lists$H_$HALLMARK_ADIPOGENESIS  )

rankorder_all2 <- rankorder_all %>%
  left_join( list_of_geneset_dfs$H_ %>%
               mutate(entrez_gene = as.character(entrez_gene)) %>%
               distinct(entrez_gene, .keep_all=T),
             by = c("id" = "entrez_gene"))


p <- plotEnrichment(geneset_lists$H_$HALLMARK_ADIPOGENESIS, ranks_list[[1]])

pdata <- p$data
pdata_more <- left_join(
  pdata ,
  rankorder_all2
) %>% arrange(rank)


make_selection2 <- function(x){
  .top <- x %>% arrange(rank) %>% filter(!is.na(ES) & !is.na(gene_symbol)) %>% head(10)
  .bot <- x %>% arrange(rank) %>% filter(!is.na(ES) & !is.na(gene_symbol)) %>% tail(10)
  return(bind_rows(.top, .bot))
}


p + geom_text_repel(data = rankorder %>% make_selection, aes(x=rank, y=ES, label = gene_symbol ), max.overlaps = Inf  )
```