---
title: "run.Rmd"
author: "BCM MSPC"
date: '`r Sys.Date()`'
output:
  html_document:
    code_folding: hide
    highlight: zenburn # pygments, kate, monochrome, zenburn
    toc: yes
    toc_float: true
params:
  volcanodir: "../results/MSPC001128/volcano/"
  rankfiledir: none
  gct_path: "../results/MSPC001128/export/MSPC001128_data_gct_all_1.0more_nonzero_normtype_median_n6x2995.gct"
  cut_by: none
  ranks_from: "volcano"  # choices are volcano and gct
  species: "Homo sapiens"
  savedir: "./plots/"
  genesets_json: >
    [
      {"category": "H", "subcategory": "", "collapse" : "FALSE"},
      {"category": "C2", "subcategory": "CP:KEGG", "collapse": "TRUE"},
      {"category": "C2", "subcategory": "CP:REACTOME", "collapse": "TRUE"},
      {"category": "C5", "subcategory": "GO:MF", "collapse" : "TRUE"},
      {"category": "C5", "subcategory": "GO:BP", "collapse" : "TRUE"},
      {"category": "C5", "subcategory": "GO:CC", "collapse" : "TRUE"} ,
      {"category": "C5", "subcategory": "All", "collapse" : "TRUE"}
    ]

---

# setup

```{r setup, include=TRUE}
suppressPackageStartupMessages(library(purrr)) # for map()
suppressPackageStartupMessages(library(magrittr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(fs)) # for dir_ls()
suppressPackageStartupMessages(library(fgsea))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(msigdbr))
suppressPackageStartupMessages(library(stringr))
suppressPackageStartupMessages(library(readr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(tictoc))
suppressPackageStartupMessages(library(ggrepel))
suppressPackageStartupMessages(library(reactable))
suppressPackageStartupMessages(library(ggalt))
# knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(future)
n_cores <- future::availableCores() - 1
future::plan(future::multisession, workers = min(n_cores, 8))

io_tools <- new.env()
source("./R/io.R", local = io_tools)

util_tools <- new.env()
source("./R/utils.R", local = util_tools)

geneset_tools <- new.env()
source("./R/geneset_utils.R", local = geneset_tools)

fgsea_tools <- new.env()
source("./R/fgsea.R", fgsea_tools)

plot_tools <- new.env()
source("./R/plot.R", local = plot_tools)

pca_tools <- new.env()
source("./R/pca.R", local = pca_tools)

savedir <- params$savedir
if (is.null(savedir)) {
  savedir <- "./plots"
}
save_func <- plot_tools$make_partial(
  plot_tools$plot_and_save,
  path = savedir
)
```
# explanations

```{r, label=test, eval=F, include=T}
# gct <- util_tools$make_random_gct()

geneset <- geneset_tools$get_collection("H", "")
geneset_list <- geneset_tools$genesets_df_to_list(geneset)
datas1 <- purrr::map(1:3, ~ fgsea_tools$simulate_preranked_data(seed = 4321))
datas1 %<>% purrr::map(~ .x %>% mutate(value = value + rnorm(nrow(.), sd = .1)))
datas2 <- purrr::map(1:3, ~ fgsea_tools$simulate_preranked_data(seed = 1234))
datas2 %<>% purrr::map(~ .x %>% mutate(value = value + rnorm(nrow(.), sd = .1)))
datas3 <- purrr::map(1:3, ~ fgsea_tools$simulate_preranked_data(seed = 9999))
datas3 %<>% purrr::map(~ .x %>% mutate(value = value + rnorm(nrow(.), sd = .1)))
datas <-
  c(
    datas1,
    datas2,
    datas3
  )
names(datas) <- paste0("test", 1:length(datas))
rankobj <- io_tools$ranks_dfs_to_lists(list(test = datas[[1]]))

.res <- rankobj[[1]] %>% fgsea_tools$run_one(geneset_list)
.name <- .res[1, "pathway"][[1]]

# enplot_data <- fgsea::plotEnrichmentData(geneset_list[[.name]], rankobj[[1]])
# .rnkorder <- -rankobj[[1]] %>% (rank)
# rankobj[[1]]['rank'] <- .rnkorder

# larger test data

genesets_of_interest <- tibble::tribble(
  ~category, ~subcategory, ~collapse,
  "H", "", FALSE,
  "C5", "GO:MF", TRUE
) %>% mutate(collection_name = stringr::str_c(category, subcategory, sep = "_")) # todo put this somewhere else

list_of_geneset_dfs <- genesets


genesets_list_of_lists <- list_of_geneset_dfs %>% purrr::map(geneset_tools$genesets_df_to_list)
rankobjs <- io_tools$ranks_dfs_to_lists(datas)


.results_list <- fgsea_tools$run_all_pathways(
  geneset_lists = genesets_list_of_lists,
  ranks = rankobjs,
  genesets_additional_info = genesets_of_interest, # dataframe with collapse indicator
  parallel = T
)
results_list <- .results_list

all_gsea_results <- plot_tools$concat_results_all_collections(results_list)
# named_data = list(data=data)




# # this doesn't work
# .gcts <- datas %>% purrr::imap(
#   ~{
#     .mat <- as.data.frame(.x)
#     rownames(.mat) <- .mat$id
#     .mat$id <- NULL
#     colnames(.mat) <- .y
#     gct <- new( "GCT",
#       mat = .mat %>% as.matrix,
#       rdesc = data.frame(row.names=rownames(.mat), id=rownames(.mat), other=seq(length(rownames(.mat))) ),
#       cdesc = data.frame(row.names=colnames(.mat), id=colnames(.mat), other=seq(length(colnames(.mat))) ),
#       cid = colnames(.mat),
#       rid = rownames(.mat)
#   )
#     #gct@version <- "# 1.3"
#     return(gct)
#   }
# )
#
# g1 <- .gcts[[1]]
# g <- g1
# g1 %>% melt_gct %>% head()
#
# g2 <- .gcts[[2]]
# g12 <- cmapR::merge_gct(g1, g2, dim = "col", matrix_only=F)# %>% merge_gct(.gcts[[3]], dim='col')
# g12@mat %>% head
#
# ( g12@cdesc %>% head )
# ( g12@rdesc %>% head )
# ( g12@mat %>% head )
#
#
# gct <- base::Reduce(accumulate=F,
#                     f=function(...) cmapR::merge_gct(..., dim = "col"),
#                     x=.gcts
# )

.datas <- datas %>% purrr::imap(~ {
  .x %>% dplyr::rename(!!.y := value)
})
# .datas[[1]] %>% head()
.mat <- base::Reduce(
  accumulate = F,
  f = function(...) full_join(..., by = "id"),
  x = .datas
) %>% as.data.frame()


rownames(.mat) <- .mat$id
.mat$id <- NULL
.meta <- data.frame(
  id = colnames(.mat),
  group = c(rep("A", 3), rep("B", 3), rep("C", 3))
)
rownames(.meta) <- .meta$id
gct <- new("GCT",
  mat = .mat %>% as.matrix(),
  cdesc = .meta
)

TESTING <- TRUE
```

## run these to examine what genesets are availabel from msigdbr


```{r, eval=F, include=T}
msigdbr::msigdbr_species()
```

```{r, eval=F, include=T}
msigdbr::msigdbr_collections()
```

# execution

## load gene sets

```{r, label='load params'}
# genesets_of_interest <- jsonlite::parse_json(params$genesets_json)
if (!exists("genesets_of_interest")) {
  genesets_of_interest <- jsonlite::fromJSON(params$genesets_json)
  genesets_of_interest <- genesets_of_interest %>% dplyr::mutate(
    collection_name = stringr::str_c(category, subcategory, sep = "_")
  )
}

species <- params$species


# SPECIES <- "Homo sapiens" # or "Mus musculus" or Saccharomyces cerevisiae, and others
# genesets_of_interest %>% purrr::map(~{print(.x$category); print(.x$subcategory)})
```


```{r, label='get genesets'}
# geneset_lists <- list_of_geneset_dfs %>% purrr::imap( ~geneset_tools$genesets_df_to_list(.x) )
if (!exists("genesets_list_of_lists")) {
  genesets_list_of_lists <- genesets_of_interest %>% purrr::map(geneset_tools$genesets_df_to_list)
}
```

## prepare ranks

```{r, label='load ranks'}
if ((!file.exists(params$volcanodir)) &
  (!file.exists(params$gct_path)) &
  (!file.exists(params$rankfiledir)) &
  (!TESTING == TRUE)) {
  print("no files present")
  knitr::knit_exit()
}
```



```{r, label='prepare ranks'}
rankfiledir <- params$rankfiledir
volcanodir <- params$volcanodir
gct_path <- params$gct_path
ranks_from <- params$ranks_from

if ((file.exists(gct_path)) && (!exists("gct"))) gct <- cmapR::parse_gctx(gct_path)

if (length(fs::dir_ls(rankfiledir, fail = F)) == 0) {
  # print('yes')
  if (ranks_from == "volcano") {
    rnkdfs <- io_tools$create_rnkfiles_from_volcano(volcanodir, value_col = "signedlogP")
  }
  if (ranks_from == "gct") {
    rnkdfs <- io_tools$create_rnkfiles_from_emat(gct_path, apply_z_score = T)
  }
  rnkdfs %>% io_tools$write_rnkfiles(dir = rankfiledir)
} # else{

# always reload rank files from new location to ensure proper format
# any format / name issues are fixed in the create_rnkfiles func
rnkfiles <- dir_ls(rankfiledir, pattern = ".rnk$", fail = F)
rnkdfs <- rnkfiles %>% io_tools$load_rnkfiles()
# print('no')
# }
names(rnkdfs) <- names(rnkdfs) %>%
  fs::path_file() %>%
  fs::path_ext_remove()

ranks_list <- rnkdfs %>% io_tools$ranks_dfs_to_lists()
```


# run fgsea
```{r, label='run fgsea', cache=T}
if (!TESTING == FALSE) {
  results_list <- fgsea_tools$run_all_pathways(genesets_list_of_lists,
    ranks_list,
    parallel = T,
    genesets_additional_info = genesets_of_interest
  ) # parallel if you c
}
# results_list2 <- .GlobalEnv$run_all_pathways(geneset_lists, ranks_list, parallel=T) # parallel if you c
```



## explore the results

results list contains a named list of pathways

```{r}
names(results_list)
```

which contain a named list of statistics

```{r}
names(results_list[[1]])
```

```{r}
head(results_list[[1]][[1]])
```



```{r, label=save}
names(results_list) %>%
  purrr::map(
    ~ {
      collection_name <- .x
      names(results_list[[collection_name]]) %>%
        purrr::map(
          ~ {
            comparison_name <- .x
            result <- results_list[[collection_name]][[comparison_name]]
            print(collection_name)
            print(comparison_name)
            outf <- paste0(make.names(collection_name), "_", make.names(comparison_name), ".tsv")
            if (!fs::file_exists(outf)) result %>% readr::write_tsv(outf)
          }
        )
    }
  )
```

## making plots


```{r}
results_list[[1]][[1]] %>%
  arrange(pval) %>%
  head(20) %>%
  plot_tools$barplot_with_numbers()
```
## plotting all barplots for each comparison within one geneset
```{r}
results_list[[1]] %>% imap(
  ~ {
    sel <- .x %>%
      arrange(pval) %>%
      head(20)
    .title <- .y %>%
      fs::path_file() %>%
      fs::path_ext_remove() # %>% gsub(pattern="_", replacement=" ", x=.)
    plot_tools$barplot_with_numbers(sel, title = .title, use_custom_labeller = T)
  }
)
```

## plotting all barplots for each comparison across all genesets
```{r, fig.width=10, fig.height=8}
plts <- results_list %>% plot_tools$all_barplots_with_numbers(save_func = save_func)
# if youw ant to print the plots:
# for (plt in plts){
#   print(plt)
# }
```

## plot facetted barplot across genesets

prewritten function to merge gsea results across comparisons and make faceted barplot
```{r, fig.width=12, fig.height=12}
plts <- results_list %>%
  plot_tools$process_results_across_rnks(
    save_func = save_func
  )

for (plt in plts) {
  print(plt)
}
```

## heatmaps of results


```{r}
all_gsea_results <- plot_tools$concat_results_all_collections(results_list)
```


```{r, fig.height=7}
ht <- all_gsea_results$H_ %>% plot_tools$plot_results_one_collection()

draw(ht,
  heatmap_legend_side = "bottom",
  padding = unit(c(2, 24, 2, 24), "mm"), # top, left, bottom, right
)
```

```{r, fig.height=9}
hts <- all_gsea_results %>% plot_tools$plot_results_all_collections()

# for (ht in hts){
#   draw(ht,
#     heatmap_legend_side = "bottom",
#     padding = unit(c(2, 24, 2, 24), "mm"), # top, left, bottom, right
#   )
# }
```


```{r, fig.height=12}
# library(org.Hs.eg.db)
# gene_symbols <- AnnotationDbi::select(org.Hs.eg.db,
#                                       keys = gct@rid
#                                       columns = c("SYMBOL"),
#                                       keytype = "ENTREZID")
# merged_data <- merge(gct@rdesc, gene_symbols, by.x = "id", by.y = "ENTREZID", all.x = TRUE)
# gct@rdesc <- merged_data


head(mat(gct))

(head(gct@rdesc))

names(results_list) %>%
  purrr::map(
    ~ {
      collection_name <- .x
      names(results_list[[collection_name]]) %>%
        purrr::map(
          ~ {
            comparison_name <- .x
            result <- results_list[[collection_name]][[comparison_name]]
            print(collection_name)
            print(comparison_name)
            forplot <- result %>%
              arrange(pval) %>%
              head(10) %>%
              mutate(leadingedgelist = stringr::str_split(leadingEdge, ","))
            for (i in 1:nrow(forplot)) {
              row <- forplot[i, ]
              .id <- row$pathway
              .leading_edge <- unlist(lapply(row$leadingedgelist, function(x) gsub('[c\\(\\)" ]', "", x)))
              .row_title <- row$pval

              print(.id)
              print(paste0("pval: ", row$pval))
              print(paste0("padj: ", row$padj))
              print(paste0("NES: ", row$NES))

              # print(.leading_edge)

              tryCatch(
                {
                  subgct <- cmapR::subset_gct(gct, rid = .leading_edge)
                  ht <- plot_tools$make_heatmap(subgct)
                  print(ht)
                },
                error = function(e) print(e$message)
              )
            }
          }
        )
    }
  )

# results_list %>%
#   purrr::imap(
#     ~{
#    collection_name <- .x
#    comparisons <- .y
#    # print(collection_name)
#    comparisons %>%
#        purrr::imap(
#             ~{
#                 gsea_res <- .x
#                 comparison_name <- .y
#                 print(comparison_name)
#                 print(gsea_res)
#                 # .row <- gsea_res %>% arrange(pval) %>% head(1)
#                 # .leading_edge <- stringr::str_split(.row$leadingEdge)
#                 # subgct <- cmapR::subset_gct( rids = .leading_edge )
#                 # print(head(mat(subgct)))
#
#              })
#   })
```

## pca and clustering


### pca

run pca
```{r}
pca_objects <- all_gsea_results %>% pca_tools$do_all()
```


```{r}
save_func <- purrr::partial(plot_tools$plot_and_save)
pca_objects[[1]] %>% pca_tools$plot_biplot(title = "first pca object", save_func = save_func)
```


```{r}
save_func <- purrr::partial(plot_tools$plot_and_save)
pca_objects %>% pca_tools$plot_all_biplots(save_func = save_func)
```



```{r, eval=F}
gct_path <- params$gct_path
gct <- cmapR::parse_gctx(gct_path)
all_gsea_results <- plot_tools$concat_results_all_collections(results_list)
.metadata <- gct@cdesc
.name <- "C5_GO:BP"


.pathways_withmeta <- all_gsea_results[[.name]] %>%
  left_join(gct@cdesc, by = c("var" = "id"))
.pathways_withmeta %<>% group_by(Model) %>%
  mutate(n_main = sum(mainpathway == T)) %>%
  mutate(ratio_main = n_main / n()) %>%
  ungroup()
# group_by(pathway) %>% summarize(n=sum(mainpathway==T)) %>% filter(n/.ntotal > .1) %>% distinct(pathway, .keep_all = T)

.ntotal <- all_res[[.name]]$var %>%
  unique() %>%
  length()
.pathways_filtered <- all_res[[.name]] %>%
  group_by(pathway) %>%
  summarize(n = sum(mainpathway == T)) %>%
  filter(n / .ntotal > .1) %>%
  distinct(pathway, .keep_all = T)
plt <- all_gsea_results[[.name]] %>%
  dplyr::filter(pathway %in% .pathways_filtered$pathway) %>%
  plot_tools$plot_results_one_collection(., metadata = .metadata, cut_by = "Model", title = .name)
```


## curve exploration


```{r, eval=F}
# Adjusting the formula with guessed parameters for a clearer sigmoid fit
# Example: a simple sigmoid with steepness and midpoint adjustments
# Ensure that you replace `.res2` and `pval` according to your actual data frame and variable names if they differ
sig_approx <- function(x) (-1 / (1 + exp(-4.1 * (x - 1.0))) + 1)

ggplot(.res2, aes(x = abs(NES), y = pval)) +
  geom_point() +
  stat_function(
    fun = sig_approx, # Adjust -0.1 (steepness) and 5 (midpoint) as needed
    color = "blue"
  ) +
  ggtitle("Fitting a Sigmoid Function")
```
```{r, eval=F}
sig_approx <- function(x) (-1 / (1 + exp(-4.1 * (x - 1.0))) + 1)
sig_approx2 <- function(x) 1 / sig_approx
sig_approx2 <- function(x) (1 + exp(-1.1 * (x - 1.0)) - 1)

ggplot(.res2, aes(y = abs(NES), x = pval)) +
  geom_point() +
  stat_function(
    fun = sig_approx2, # Adjust -0.1 (steepness) and 5 (midpoint) as needed
    color = "blue"
  ) +
  ggtitle("Fitting a Sigmoid Function")
```


## plot large tabular plots

this is slow
```{r, fig.width=10, fig.height=12, eval=F}
res <- plot_tools$plot_tables(
  results_list = results_list,
  ranks_list = ranks_list,
  pathways_list = pathways_list_of_lists
)
```

## examine rankorder


```{r}
# rankorder <- .GlobalEnv$get_rankorder(ranks_list[[1]], geneset_lists[[1]][[1]]  )


genesets_of_interest <- genesets_list_of_lists[[1]]
rankobject <- rankobjs[[1]]
# enplot_data <- plotEnrichmentData(genesets_of_interest[[1]], rankobject)
collection_name <- names(genesets_list_of_lists)[[1]]
geneset_of_interest_name <- names(genesets_of_interest)[[1]]

# enplot_raw <- plotEnrichment(genesets_of_interest[[1]], rankobject)
# enplot_data <- plotEnrichmentData(genesets_of_interest[[1]], rankobject)

rankorder_object <- fgsea_tools$get_rankorder(
  genesets_of_interest[[1]], rankobject,
  list_of_geneset_dfs[[collection_name]]
)

rankorder_object %>% plot_tools$plotES() +
  labs(title = geneset_of_interest_name)
```
```{r}
make_selection <- function(x) {
  x <- x %>% arrange(rank)
  es_min <- x %>%
    pull(ES) %>%
    min(na.rm = T)
  es_max <- x %>%
    pull(ES) %>%
    max(na.rm = T)
  .first <- which(x$ES == es_min)
  .second <- which(x$ES == es_max)
  .bot <- x %>% tail(dim(x)[1] - .first)
  .top <- x %>% head(.second)
  browser()
  return(bind_rows(.top, .bot))
}

with(
  rankorder_object,
  ggplot(data = curve) +
    geom_line(aes(x = rank, y = ES), color = "green") +
    # geom_ribbon(
    #   data = stats,
    #   mapping = aes(
    #     x = rank, ymin = 0,
    #     ymax = stat / maxAbsStat * (spreadES / 4)
    #   ),
    #   fill = "grey"
    # ) +
    geom_segment(
      data = ticks,
      mapping = aes(
        x = rank, y = -spreadES / 16,
        xend = rank, yend = spreadES / 16
      ),
      size = 0.2
    ) +
    geom_hline(yintercept = posES, colour = "red", linetype = "dashed") +
    geom_hline(yintercept = negES, colour = "red", linetype = "dashed") +
    geom_hline(yintercept = 0, colour = "black") +
    theme(
      panel.background = element_blank(),
      panel.grid.major = element_line(color = "grey92")
    ) +
    labs(x = "rank", y = "enrichment score") +
    geom_text_repel(
      mapping = aes(x = rank, y = ES, label = gene_symbol), data = edge %>% filter(rank %in% ticks$rank) %>% make_selection(),
      max.overlaps = Inf, max.time = 4
    )
  # geom_text_repel( mapping = aes(x = rank, y = ES, label = gene_symbol), data = edge %>% filter(rank %in% ticks$rank) )
)
```



```{r}
rankorder_object <- fgsea_tools$get_rankorder(genesets_of_interest[[1]], rankobject)

enplot_data <- plotEnrichmentData(genesets_of_interest[[1]], rankobject)

.for_merge <- list_of_geneset_dfs[[collection_name]] %>%
  filter(gs_name == geneset_of_interest_name) %>%
  mutate(entrez_gene = as.character(entrez_gene)) %>%
  distinct(entrez_gene, .keep_all = T) # sometimes there's a duplicate annotate (maybe because multiple ensembl gids)


.rankorder <- rankorder_object$edge %>% left_join(
  .for_merge,
  by = c("id" = "entrez_gene")
)
rankorder_object$edge <- .rankorder # %>% filter(!is.na(stat_tick))
rankorder_object$stats <- .rankorder # %>% filter(!is.na(stat_tick))

rankorder_object$edge %>%
  make_selection() %>%
  dim()

plot_tools$edgeplot1(rankorder_object = rankorder_object) +
  geom_text_repel(data = . %>% filter(!is.na(stat_tick)) %>% make_selection(), aes(label = gene_symbol), max.overlaps = Inf)
```

```{r}
plot_tools$edgeplot1(rankorder_object = rankorder_object) +
  geom_text_repel(data = . %>% filter(!is.na(stat_tick)) %>% make_selection(), aes(label = gene_symbol), max.overlaps = Inf)
```

```{r, fig.width=10, fig.height=8, eval=F}
make_selection <- function(x) {
  es_min <- x %>%
    pull(ES) %>%
    min(na.rm = T)
  es_max <- x %>%
    pull(ES) %>%
    max(na.rm = T)
  .first <- which(x$ES == es_min)
  .second <- which(x$ES == es_max)
  .top <- x %>%
    arrange(rank) %>%
    head(.first)
  .bot <- x %>%
    arrange(rank) %>%
    tail(dim(x)[1] - .second)
  return(bind_rows(.top, .bot))
}
```

```{r, fig.width=10, fig.height=8, eval=F}  
rankorder %<>% arrange(stat_tick)
rankorder %>%
  plot_tools$edgeplot1() +
  geom_text_repel(data = . %>% make_selection(), aes(label = gene_symbol), max.overlaps = Inf)
```



```{r, fig.width=12, fig.height=10, eval=F}
# rankorder_all <- .GlobalEnv$get_rankorder(ranks_list[[1]], pathways_list_of_lists$H_$HALLMARK_ADIPOGENESIS  )

rankorder_all <- fgsea_tools$get_rankorder(ranks_list[[1]], pathways_list_of_lists$H_$HALLMARK_ADIPOGENESIS)

rankorder_all2 <- rankorder_all %>%
  left_join(
    list_of_geneset_dfs$H_ %>%
      mutate(entrez_gene = as.character(entrez_gene)) %>%
      distinct(entrez_gene, .keep_all = T),
    by = c("id" = "entrez_gene")
  )



pdata <- p$data
pdata_more <- left_join(
  pdata,
  rankorder_all2
) %>% arrange(rank)


make_selection2 <- function(x) {
  .top <- x %>%
    arrange(rank) %>%
    filter(!is.na(ES) & !is.na(gene_symbol)) %>%
    head(10)
  .bot <- x %>%
    arrange(rank) %>%
    filter(!is.na(ES) & !is.na(gene_symbol)) %>%
    tail(10)
  return(bind_rows(.top, .bot))
}


p <- fgsea::plotEnrichment(pathways_list_of_lists$H_$HALLMARK_ADIPOGENESIS, ranks_list[[1]])
p + geom_text_repel(data = rankorder %>% make_selection(), aes(x = rank, y = ES, label = gene_symbol), max.overlaps = Inf)
# print(p)
```
